Defending Against Web Application Attacks: Research Approaches, Challenges and Implications

### 2016-02-25 docs/questioning.tex
minor changes

% \begin{figure}[t]
% \begin{center}
% \leavevmode
% \includegraphics[scale=0.47]{defect-percentages.png}
% \end{center}
% \caption{\label{fig:defect_sources}Most common sources of real-world vulnerabilities
% used for testing of web attack defenses.
% Specifically, the publications that used a particular source are as follows:
% {\sc cve}~\cite{XBS06,NLC07,PMP11,BK04,BV08,JB07,SMS13,WPLKK09,JKK06a,PS11},
% {\it Bugtraq}~\cite{PB05,KKVJ06,JEP08},
% {\sc xss}ed.com~\cite{NSS06,APKLM10},
% ha.ckers.org~\cite{TNH07,PSC09,LV09},
% Microsoft~\cite{RDWDE07}.}
% \end{figure}

% \begin{figure}[t]
% \begin{center}
% \leavevmode
% \includegraphics[scale=0.57]{defect-percentages.png}
% \end{center}
% \caption{\label{fig:defect_sources}Most common sources of real-world vulnerabilities
% used for testing of web attack defenses.
% Specifically, the publications that used a particular source are as follows:}
% \scriptsize \Note{{\sc cve}~\cite{XBS06,NLC07,PMP11,BK04,BV08,JB07,SMS13,WPLKK09,JKK06a,PS11},}
% \scriptsize \Note{Bugtraq~\cite{PB05,KKVJ06,JEP08},}
% \scriptsize \Note{{\sc xss}ed.com~\cite{NSS06,APKLM10},}
% \scriptsize \Note{ha.ckers.org~\cite{TNH07,PSC09,LV09},}
% \scriptsize \Note{Microsoft~\cite{RDWDE07}.}
% \end{figure}

>>>>

\begin{figure}[t]
\begin{center}
\leavevmode
\includegraphics[scale=0.47]{defect-percentages.png}
\end{center}
\caption{\label{fig:defect_sources}Most common sources of real-world vulnerabilities
used for testing of web attack defenses.
Specifically, the publications that used a particular source are as follows:
{\sc cve}~\cite{XBS06,NLC07,PMP11,BK04,BV08,JB07,SMS13,WPLKK09,JKK06a,PS11},
Bugtraq~\cite{PB05,KKVJ06,JEP08},
{\sc xss}ed.com~\cite{NSS06,APKLM10},
ha.ckers.org~\cite{TNH07,PSC09,LV09},
Microsoft~\cite{RDWDE07}.}
\end{figure}
